Prefetching SPARQL query cacher

### 2016-05-04 dissertation/cache-proxy.tex
relevant modules to the project

\documentclass[a4paper, 12pt, draft]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

\include{notasjon}
\include{helpers}
\usepackage[pdftex,linktocpage]{hyperref}

@@

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\newcommand{\todo}[1]{\ensuremath{^{\textrm{\tiny{TODO}\normalsize}}}\footnote{\textbf{TODO:}~#1}}

\include{notasjon}
\include{helpers}
\usepackage[pdftex,linktocpage]{hyperref}
\hyperbaseurl{https://github.com/}

@@

\section{Implementation}\label{sec:impl}

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. As
such, it builds on the code of hundreds of authors, too long to
enumerate. I shall constrain myself to list the modules that have code
that has been motivated from this study. Modules that have other
primary authors than myself have been started prior to this present
project, but may have substantial contributions from this project. The
Attean framework was started as part of the effort in
Section~\ref{sec:conpush}, but even though it has been developed
further with the requirements that arose from this project and has
contributions from me, the vast majority of the code has been written
my Gregory Todd Williams. The main work in this project has gone into
the module AtteanX::Query::Cache, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{see \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

\begin{table}
\caption{The modules that enable the query cache}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

  AtteanX::Query::Cache & Kjetil Kjernsmo, Gregory Todd Williams &
  \url{kjetilk/p5-atteanx-query-cache} \\

  AtteanX::Store::SPARQL & Kjetil Kjernsmo &
  \url{kjetilk/p5-atteanx-store-sparql} \\

  AtteanX::Store::LDF & Kjetil Kjernsmo, Patrick Hochstenbach &
  \url{phochste/AtteanX-Store-LDF} \\

  LWP::UserAgent::CHICaching & Kjetil Kjernsmo &
  \url{kjetilk/p5-lwp-useragent-chicaching} \\

  Attean & Gregory Todd Williams, Kjetil Kjernsmo &
  \url{kasei/attean} \\

  AtteanX::Endpoint & Gregory Todd Williams &
  \url{kasei/atteanx-endpoint} \\

  RDF::LDF &  Patrick Hochstenbach, Gregory Todd Williams, Jakob Voß,
  Kjetil Kjernsmo & \url{phochste/RDF-LDF} \\

  \hline
\end{tabular}
\end{table}

The system also depends on modules I have written that is not part of
the project: RDF::LinkedData, RDF::Generator::Void, Test::RDF,
URI::NamespaceMap and RDF::NS::Curated.
